Analysis of gene regulatory properties underlying trait pleiotropy

### 2022-10-17 presentation_gold2022_paris/presentation_gold2022_paris.tex
ENH finished refactoring class

\begin{columns}
\begin{column}{0.32\textwidth}
    \begin{center}
\includegraphics[width=\textwidth]{/home/gonzalez/Repositories/gwas2eqtl_pleiotropy/out/gwas418/pval_5e-08/r2_0.1/kb_1000/window_1000000/pltsctr_x_per_rsid_y_gwas.py/count_per_rsid_chr19_start48668049_end48756272_categories8.png}
     \end{center}
\end{column}
\begin{column}{0.32\textwidth}
    \begin{center}
\includegraphics[width=\textwidth]{/home/gonzalez/Repositories/gwas2eqtl_pleiotropy/out/gwas418/pval_5e-08/r2_0.1/kb_1000/window_1000000/pltsctr_x_per_rsid_y_egene.py/count_per_rsid_chr19_start48668049_end48756272_categories8.png}
     \end{center}
\end{column}
\begin{column}{0.32\textwidth}
    \begin{center}
\includegraphics[width=\textwidth]{/home/gonzalez/Repositories/gwas2eqtl_pleiotropy/out/gwas418/pval_5e-08/r2_0.1/kb_1000/window_1000000/pltsctr_x_per_rsid_y_egene.py/count_per_rsid_chr19_start48668049_end48756272_categories8.png}
     \end{center}
\end{column}
\end{columns}
%
\vfill
%
Neighboring variants show similar pleiotropy.

>>>>

\begin{columns}
\begin{column}{0.32\textwidth}
    \begin{center}
\includegraphics[width=\textwidth]{/home/gonzalez/Repositories/gwas2eqtl_pleiotropy/out/gwas418/pval_5e-08/r2_0.1/kb_1000/window_1000000/pltsctr_x_per_rsid_y_gwas.py/count_per_rsid_chr5_start131912097_end132802472_categories7.png}
     \end{center}
\end{column}
\begin{column}{0.32\textwidth}
    \begin{center}
\includegraphics[width=\textwidth]{/home/gonzalez/Repositories/gwas2eqtl_pleiotropy/out/gwas418/pval_5e-08/r2_0.1/kb_1000/window_1000000/pltsctr_x_per_rsid_y_egene.py/count_per_rsid_chr5_start131912097_end132802472_categories7.png}
     \end{center}
\end{column}
\begin{column}{0.32\textwidth}
    \begin{center}
\includegraphics[width=\textwidth]{/home/gonzalez/Repositories/gwas2eqtl_pleiotropy/out/gwas418/pval_5e-08/r2_0.1/kb_1000/window_1000000/pltsctr_x_per_rsid_y_egene.py/count_per_rsid_chr5_start131912097_end132802472_categories7.png}
     \end{center}
\end{column}
\end{columns}
%
\vfill
%
Neighboring variants show similar pleiotropy.
